Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed

### 2023-02-19 outputs/paper/paper.qmd
Edits to data section and additional references

Sociodemographics:

-   Age Group

-   Gender

-   State

-   German Citizen

-   Marital Status

-   Relationship status, single

-   Religious Affiliation

-   Education

-   Occupation

-   Income

-   Household Size

-   Subjective Social Status

-   Male population: determining states with access to males by dividing the number of women by men aged 14 and 44 for each municipality

-   Politics: left and right-leaning

-   Politics: affiliated parties

Mate Competition: using a scale of agree or disagree

-   Does the influx of male refugees make it difficult for non-immigrant german men to find female partners

Job Competition: using a scale of agree or disagree

-   The inflow of young make refugees make it more difficult for young non-immigrant German men to find work/ jobs

Life Satisfaction: scale of 0-10

@@

Encountering Refugees

-   How many KM is the closest refugee reception center from your home \* How many refugees do you believe have settled in your municipality in the last year \* In the last month, how many refugees have you encountered in the following locations

Attitudes Toward Refugees (national and local scale): using a scale of agree or disagree

-   Violence is sometimes the only means that citizens have to get the attention of German politicians \* Attitudes towards Muslims

@@

Operational category

>>>>

[Socio-demographics]{.underline}

-   Age Group
-   Gender
-   State
-   German Citizen
-   Marital Status
-   Relationship status, single
-   Religious Affiliation
-   Education
-   Occupation
-   Income
-   Household Size
-   Subjective Social Status
-   Male population: determining states with access to males by dividing the number of women by men aged 14 and 44 for each municipality
-   Politics: left and right-leaning
-   Politics: affiliated parties

[Mate Competition: using a scale of agree or disagree]{.underline}

-   Does the influx of male refugees make it difficult for non-immigrant german men to find female partners
-   Job Competition: using a scale of agree or disagree
-   The inflow of young make refugees make it more difficult for young non-immigrant German men to find work/ jobs

[Life Satisfaction: scale of 0-10]{.underline}

@@

[Encountering Refugees]{.underline}

-   How many KM is the closest refugee reception center from your home

-   How many refugees do you believe have settled in your municipality in the last year

-   In the last month, how many refugees have you encountered in the following locations

[Attitudes Toward Refugees (national and local scale): using a scale of agree or disagree]{.underline} -

-   Violence is sometimes the only means that citizens have to get the attention of German politicians - Attitudes towards Muslims

@@

[Operational category]{.underline}
